Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-04-10 src/tex/ms.tex
[showyourwork] overleaf sync

% Filler text
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{showyourwork}
\usepackage{amssymb}
\usepackage{siunitx}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\arcsinh}{arcsinh}
\newcommand{\chandra}{\textit{Chandra}~}
\newcommand{\xmm}{\textit{XMM}~}
\newcommand{\fermi}{\textit{Fermi}-LAT~}
\newcommand{\jolideco}{\textit{Jolideco}~}
\newcommand{\aposteriori}{a~posteriori~}
\newcommand{\gammaray}{$\gamma$-ray\xspace}
\newcommand{\xray}{X-ray\xspace}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

    \section{Introduction}
    The angular resolution of any physical or astronomical imaging process is inherently limited by the instrument or telescope used. Furthermore, the quality of the resulting image is affected by background or instrumental measurement noise and non-uniform exposure. This is especially true in the low signal-to-noise regime. E.g. \xray and \gammaray~astronomy

    In literature there have been multiple efforts to correct the degrading of the images
    and maximise the scientific use.

    Any astronomical observation is affected by the limited angular resolution of the telescope. However the problem is not specific to astronomy and has been tried to 
    be solved for fluorescence microscopy or others...

    We assume non-blind deconvolution, so the there is prior information of the PSF

    \begin{itemize}
        \item Standard baseline method is Richardson \& Lucy (RL), see \cite{Richardson1972} and \cite{Lucy1974}
         \item  Problem of RL decomposing structures into point sources: \cite{Reeves1994} \cite{Fish1995}
         \item regularised RL , e.g. total variation \citep{Dey2006} or maximum entropy \citep{Bi1994} \todo{other references?}
        \item Joint likelihood RL: \cite{Ingaramo2014} has found that RL take the best out of each image and create a "merged" image
        \item Multi-scale LIRA prior of course: \cite{Esch2004, Connors2011}, advantage of error estimates / Bayesian sampling. However prior is rather "ad-hoc", no physical information / assumptions. Just "smoothness"
        \item What abput d3po and d4po? Priors based on physical assumptions, decomposition into point and diffuse flux, but in 3d/4d \cite{Selig2015}\cite{Pumpe2018}. The smoothness assumption works for large scale emission, but leads to artifacts in the galactic plane... 
    \end{itemize}

@@

    \subsection{A note on Deep Learning Methods}
    \cite{Li2014} have introduced a baseline architecture for a deep convolutional neural network for image deblurring.
    The convolutional nature of the network does not make it suitable for the task. As convolution introduces smoothing.
    However the network can learn an "inverse kernel", which needs to be larger because of the uncertainty principle (\todo{reference...}).
    The large kernels are introduced by separability assumption...
    In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possibly for most network architectures. Except for e.g. normalising flows \todo{there are references where NFs have bee used as priors...}

@@

    Shown to work for e.g. deconvolution of Galaxy images SDSS \todo{reference?} and post-processing of regularised RL results \todo{Starck et al.}

@@

    \begin{itemize}
        \item the case of non-overlapping patches is rather simple
        \item for overlapping patches we have to make a few more approximations
        \item either we neglect the correlation between overlapping patches
        \item or we have to optimize the array of $\mathbf{k}$ at the same time, instead of "per patch optimization". However optimization on discrete 
        values is not easily possible in Pytorch. However here is one idea:
        group the GMM components by similarity and introduce a single continues
        parameter $z$, which interpolates between similar components. 
        \item we also compute the mean of the likelihood for the overlapping parts
    \end{itemize}

@@

    \begin{figure}[ht!]
        \script{patches.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/patches.pdf}
            \caption{
                Grid of overlapping patches of size 8x8 pixels. The overlap size was chosen to be 2 pixels.
            }
            \label{fig:patches}
        \end{centering}
    \end{figure}

@@

    The GMM patch prior is learned from other images whose pixel intensities
    have no physical relationship of the intensities of the Poisson data we are
    dealing with. To overcome this the GMM is learned on normalized images,
    where the intensity values are constrained between 0 and 1.
    To evaluate the GMM patch prior on the 
    model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
    in the same dynamic range between 0 and 1. Multiple common choices for such a
    mapping function are shown in Fig.~\ref{fig:image-norms}.

    \begin{figure}[ht!]
        \script{image-norms.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/image-norms.pdf}
            \caption{
                Various image norms with different dynamic behaviour.
            }
            \label{fig:image-norms}
        \end{centering}
    \end{figure}

@@

    Alternatively we used a \textit{data augmentation} approach to learn a GMM prior with a randomized direction of the jet. For this we rotated the jet image after alignment by 
    a random angle. Then again we split each image into patches of size 8x8 pixels. In total we created \todo{insert number} patches and learned a GMM with 64 components. The prior
    is adapted to the analysis scenario of jet detection, where no no prior knowledge on the
    direction is available.

@@

    \subsection{Optimization Strategy}
    In practice we employ the following optimization strategy:
    \begin{itemize}
        \item the optimizer sees $\log{\mathbf{x}}$
        \item First run with uniform prior, to get a rough estimate
        \item (optional) Then optimize the parameters associated to the systematic error described in Eq.~\ref{eq:model-npred-calibration}.
        \item Then we go for a full optimization using the patch prior, which can be computationally costly
        \item we use ADAM (stochastic gradient decent), without decay
        \item  (optional) learning rate scheduling? So far just a fixed step size value of $1e-3$
    \end{itemize}

    \section{Experiments}
    \subsection{Test Datasets}
    \todo{Vinay writes this?}
    \vlk{yes}

    \vlk{We have devised four distinct arrangements of combinations of point and extended sources of differents shapes to test the algorithms.  The arrangements are 
    \begin{itemize}
        \item[ ``Gauss":] A set of four point sources arranged around an extended Gaussian source
        \item[``Points":] Point sources arranged with different separations
        \item[``Shield":] Disk shaped flat extended source with superposed point sources and linear jet-like features
        \item[``Spiral":] Extended thin double-spiral with a flat disk at the center and point sources adjacent to it
    \end{itemize}
    The arrangements are shown in Figure~TBD, and the details of the locations and brightness of each component is listed in Table~TBD.
    }

@@

    \begin{figure*}[ht!]
        \script{example-chandra.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-chandra.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-chandra}
        \end{centering}
    \end{figure*}

    \subsection{Combined \xmm and \chandra Observation}
    \begin{figure*}[ht!]
        \script{example-xmm-chandra.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-xmm-chandra.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-xmm-chandra}
        \end{centering}
    \end{figure*}

@@

    We chose the patch prior learned on the GLEAM data, described in the Section~\ref{sssec:gleam-radio-data}
    and a linear scaling. 
    As a background model we included the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits}.

    For the data reduction we use the fermitools \todo{add version} and Gammapy v1.0 \cite{Gammapyv1.0}.
    While the fermitools output an energy dependent counts, exposure and background cube, we use Gammapy
    to reduce to and image, assuming a power law with index $\Gamma=1.77$ \citep{Ajello2017} as spectral model to compute the effective PSF and exposure. To preserve the information on the angular resolution we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}

@@

    \begin{figure*}[ht!]
        \script{example-fermi-lat.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-fermi-lat.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-fermi-lat}
        \end{centering}
    \end{figure*}

    \section{Reproducibility}
    In order to facilitate reproducibility we make source code for the paper and figures  available at \url{https://github.com/jolideco/jolideco-paper}.
    The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021}. See instructions 
    All data is available on Zenodo \todo{how do we do this exactly...?}

@@

    \begin{itemize}
        \item Extend \jolideco to handle spectral dimension at the same time.
        \item Use normalising flows for patch priors see \cite{Altekrueger2022}
        \item Use other mixture models, such as Student T or generalised Gaussian. 
        \item one could try deep image priors \citep{Ulyanov2017}
        \item Extend to use GMM patch prior on multiple scales, see \cite{Papyan2015}
    \end{itemize}

    \section*{Acknowledgements}
    This work was conducted under the auspices of the CHASC International Astrostatistics Center.
    CHASC is supported by NSF grants DMS-21-13615, DMS-21-13397, and DMS-21-13605; by the UK Engineering
    and Physical Sciences Research Council [EP/W015080/1]; and by NASA APRA Grant 80-NSSC21-K0285.
    We thank CHASC members for many helpful discussions, especially Xiao-Li Meng and Katy McKeough.
    DvD was also supported in part by a Marie-Skodowska-Curie RISE Grant (H2020-MSCA-RISE-2019-873089)
    provided by the European Commission.
    Aneta Siemiginowska, Vinay Kashyap, and Doug Burke further acknowledge support from NASA
    contract to the Chandra X-ray Center NAS8-03060.

>>>>

% Filler text
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{showyourwork}
\usepackage{amssymb}
\let\tablenum\relaxgit 
\usepackage{siunitx}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\arcsinh}{arcsinh}
\newcommand{\chandra}{\textit{Chandra}~}
\newcommand{\xmm}{\textit{XMM}~}
\newcommand{\fermi}{\textit{Fermi}-LAT~}
\newcommand{\jolideco}{\textit{Jolideco}~}
\newcommand{\aposteriori}{a~posteriori~}
\newcommand{\gammaray}{$\gamma$-ray\xspace}
\newcommand{\xray}{X-ray\xspace}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

    \section{Introduction}
    The angular resolution of any physical or astronomical imaging process is inherently limited by the instrument or telescope used.
    Furthermore, the quality of the resulting image is affected by background or instrumental measurement noise and non-uniform exposure. This is especially true in the low signal-to-noise regime, where images are affected by Poisson noise.

    Such as images taken by \xray and \gammaray~astronomy but also to other fields such as

    To maximise the scientific use of available data it is desirable to correct for the instrumental imprint on the data.

    We assume non-blind deconvolution, so the there is prior information of the point spread function (PSF). The PSF can be estimated empirically from observation of known point sources, such as distant activate galactic nuclei or a model of the PSF can obtained from simulation of the instrument.

    This class of problems is called inverse problems.

    \subsection{Related Work}
    In literature there have been multiple efforts to correct the degrading of the images using statistical methods.
    The standard baseline method for image deconvolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974}. They used expectation maximisation to solve. We will refer to this method as "RL".

    One of the significant challenges in image deconvolution is the problem of Rayleigh-Lynden Bell (RL) decomposition of structures into point sources. This problem was first introduced by Reeves et al. \cite{Reeves1994} and later analyzed by Fish et al. \cite{Fish1995}. Regularized RL methods, such as total variation \citep{Dey2006} and maximum entropy \citep{Bi1994}, have been proposed to overcome this issue.

    Multi-scale LIRA prior has been used in image deconvolution to incorporate error estimates and Bayesian sampling. This prior has been used in various studies, including those by Esch et al. \cite{Esch2004} and Connors et al. \cite{Connors2011}. However, the prior is ad-hoc and lacks physical information or assumptions, limiting its applicability.

    Another approach to image deconvolution is joint likelihood RL, which has been shown to be effective in creating a merged image from multiple images \cite{Ingaramo2014}. In this approach, RL takes the best out of each image and merges them to create a more accurate representation of the object.

    An alternative approach to solve the problem in the framework of information field theory.

    Recently, image deconvolution using physical assumptions and decomposition into point and diffuse flux in 3D/4D has gained attention. Pumpe et al. \cite{Pumpe2018} and Selig et al. \cite{Selig2015} proposed priors based on physical assumptions, which have been shown to work well for large-scale emission. However, the smoothness assumption in these methods can lead to artifacts in the galactic plane.

    The challenge is due to fundamentally contradicting goals: deconvolution favoring point sources will decompose extend structures,
    while introducing local correlations will lead to

    \begin{itemize}
         \item  Problem of RL decomposing structures into point sources: \cite{Reeves1994} \cite{Fish1995}
         \item regularised RL , e.g. total variation \citep{Dey2006} or maximum entropy \citep{Bi1994} \todo{other references?}
        \item Joint likelihood RL: \cite{Ingaramo2014} has found that RL take the best out of each image and create a "merged" image
        \item Multi-scale LIRA prior of course: \cite{Esch2004, Connors2011}, advantage of error estimates / Bayesian sampling. However prior is rather "ad-hoc", no physical information / assumptions. Just "smoothness"
        \item What abput d3po and d4po? Priors based on physical assumptions, decomposition into point and diffuse flux, but in 3d/4d \cite{Selig2015}\cite{Pumpe2018}. The smoothness assumption works for large scale emission, but leads to artifacts in the galactic plane... 
    \end{itemize}

@@

    \subsection{A note on Deep Learning Methods}
    In the past decade Machine learning (ML) especially deep convolutional neural networks became the \textit{de facto} standard
    for de-blurring and super-resolution of natural images \todo{reference review?}. However their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning. For a variety of reasons this approach is not suitable for astronomical x-ray and \gammaray data.

    Astronomical data is rare and expensive and there is no ground truth. One could rely on transfer learning and simulated data. E.g. radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise. However astronomical images have a large dynamic range and show a high diversity in morphological structure, which would still require al large amount of training data. However this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \todo{reference} or as a post processing step of results obtained with regularised RL \todo{Reference by Starck et al.}.

    In addition to the challenge of obtaining training data, it is known that the PSF of instruments such as \chandra is highly variable. It varies with observation conditions and depends e.g. on energy as well as offset angle from the pointing direction. To cover the whole parameter space of the PSF one would need to train a network for each of the PSF models, which would require a very large computational effort.

    \cite{Li2014} have introduced a baseline architecture for a deep convolutional neural network for image deblurring.
    The convolutional nature of the network does not make it suitable for the task. As convolution introduces smoothing.
    However the network can learn an "inverse kernel", which needs to be larger because of the uncertainty principle (\todo{reference...}).
    The large kernels are introduced by separability assumption...
    In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possibly for most network architectures. Except for e.g. normalising flows \todo{there are references where NFs have bee used as priors...}

@@

@@

    \begin{itemize}
        \item the case of non-overlapping patches is rather simple
        \item for overlapping patches we have to make a few more approximations
        \item either we neglect the correlation between overlapping patches
        \item or we have to optimize the array of $\mathbf{k}$ at the same time, instead of "per patch optimization". However optimization on discrete 
        values is not easily possible in Pytorch. However here is one idea:
        group the GMM components by similarity and introduce a single continues
        parameter $z$, which interpolates between similar components.
        \item Another idea is to use "Gumbel Softmax"...
        \item we also compute the mean of the likelihood for the overlapping parts
    \end{itemize}

@@

    \begin{figure}
        \script{patches.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/patches.pdf}
            \caption{
                Grid of overlapping patches of size 8x8 pixels. The overlap size was chosen to be 2 pixels.
            }
            \label{fig:patches}
        \end{centering}
    \end{figure}

@@

    \begin{equation}
        \tilde{\mathbf{x}}_n = f \left(\frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n} \right)
    \end{equation}

    With a given non-linearity:

    \begin{equation}
        f(x) = \arcsinh{x / \alpha}
    \end{equation}

    \todo{The patch normalisation remains to be decided, but it would be advantageous to get rid of the hyper-parameter associated with the total image normalisation}.
    The GMM patch prior is learned from other images whose pixel intensities
    have no physical relationship of the intensities of the Poisson data we are
    dealing with. To overcome this the GMM is learned on normalized images,
    where the intensity values are constrained between 0 and 1.
    To evaluate the GMM patch prior on the 
    model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
    in the same dynamic range between 0 and 1. Multiple common choices for such a
    mapping function are shown in Fig.~\ref{fig:image-norms}.

    \begin{figure}
        \script{image-norms.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/image-norms.pdf}
            \caption{
                Various image norms with different dynamic behaviour.
            }
            \label{fig:image-norms}
        \end{centering}
    \end{figure}

@@

    Alternatively we used a \textit{data augmentation} approach to learn a GMM prior with a randomized direction of the jet. For this we rotated the jet image after alignment by 
    a random angle. Then again we split each image into patches of size 8x8 pixels. In total we created \todo{insert number} patches and learned a GMM with 64 components. The prior
    is adapted to the analysis scenario of jet detection, where no prior knowledge on the
    direction is available.

    \begin{figure}
        \script{gmm-eigen-images.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/gmm-eigen-images.pdf}
            \caption{
                Eigenimages of the covariance matrices of the 32 components of the GMM learned from the NRAO jets. \todo{Provide other examples...?!?}
            }
            \label{fig:gmm-eigen-images}
        \end{centering}
    \end{figure}

    \subsubsection{Chandra SNRs}

    Learn prior from \chandra images of supernova remnants (SNRs).  Self-similarity

@@

    \subsection{Optimization Strategy}
    Maximising the \aposteriori likelihood defined Eq.\ref{eq:total} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem. To improve the convergence rate of the optimization process we employ the following optimization strategy: the optimization strategy begins with the optimizer viewing $\log{\mathbf{x}}$, and the first step involves running a rough estimate using a uniform prior. This step is optional, but if chosen, the next step involves optimizing the parameters associated with the systematic error described in Eq.~\ref{eq:model-npred-calibration}. Following this, a full optimization is performed using the patch prior, which can be computationally expensive. The optimization algorithm used is ADAM, a stochastic gradient descent method, without decay. Finally, there is an optional step of learning rate scheduling, although so far, a fixed step size value of $1e-3$ has been used.

    In practice we employ the following optimization strategy:
    \begin{itemize}
        \item the optimizer sees $\log{\mathbf{x}}$
        \item First run with uniform prior, to get a rough estimate
        \item (optional) Then optimize the parameters associated to the systematic error described in Eq.~\ref{eq:model-npred-calibration}.
        \item Then we go for a full optimization using the patch prior, which can be computationally costly
        \item we use ADAM (stochastic gradient decent), without decay
        \item  (optional) learning rate scheduling? So far just a fixed step size value of $1e-3$
    \end{itemize}

    \section{Experiments}
    \subsection{Test Datasets}\label{sec:testmodels}
    \todo{Vinay writes this?}
    \vlk{yes}

    \vlk{We have devised four distinct arrangements of combinations of point and extended sources of differents shapes to test the algorithms.  The arrangements are 
    \begin{itemize}
        \item[(A)] {\bf asterism:} A set of four point sources arranged around an extended Gaussian source
        \item[(B)] {\bf points:} Point sources arranged with different separations
        \item[(C)] {\bf shield:} Disk shaped flat extended source with superposed point sources and linear jet-like features
        \item[(D)] {\bf spiral:} Extended thin double-spiral with a flat disk at the center and point sources adjacent to it
    \end{itemize}
    The arrangements are shown in Figure~TBD, and the details of the locations and brightness of each component is listed in Table~TBD.

    \begin{figure*}
        \centering\includegraphics{figures/chandra_gauss_fwhm4710_128x128_aster1+point1+disk1+spiral3.pdf}
        \caption{Illustrating the source patterns used to make test datasets.  The patterns shown are for the {\sl (A)} {\tt asterism}, {\sl (B)} {\tt points}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}), convolved with a sharp PSF (Gaussian with $\sigma=2$~pix).  All images are of size $128{\times}128$.  The dashed red and magenta boxes depict $32{\times}32$ and $64{\times}64$ regions of interest.  Note that the boxes are displaced to the lower left corner in Case B, and leftwards in Case D.}
        \label{fig:simulated_models_chandra}
    \end{figure*}
     \begin{figure*}
        \centering\includegraphics{figures/xmm_gauss_fwhm14130_128x128_aster1+point1+disk1+spiral3.pdf}
        \caption{As in Figure~\ref{fig:simulated_models_chandra}, convolved with a diffuse PSF (Gaussian with $\sigma=6$~pix).}
        \label{fig:simulated_models_xmm}
    \end{figure*}
    }

@@

    \begin{figure*}
        \script{example-chandra.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-chandra.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-chandra}
        \end{centering}
    \end{figure*}

    \subsection{Combined \xmm and \chandra Observation}
    \begin{figure*}
        \script{example-xmm-chandra.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-xmm-chandra.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-xmm-chandra}
        \end{centering}
    \end{figure*}

@@

    We chose the patch prior learned on the GLEAM data, described in the Section~\ref{sssec:gleam-radio-data}
    and a linear scaling. 
    As a background model we included the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and nearby sources from the 3FHL catalog \cite{Ajello2017}.

    For the data reduction we use the fermitools \todo{add version} and Gammapy v1.0 \cite{Gammapyv1.0}.
    While the fermitools output an energy dependent counts, exposure and background cube, we use Gammapy
    to reduce to and image, assuming a power law with index $\Gamma=1.77$ \citep{Ajello2017} as spectral model to compute the effective PSF and exposure. To preserve the information on the angular resolution we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}.

@@

    \begin{figure*}
        \script{example-fermi-lat.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-fermi-lat.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-fermi-lat}
        \end{centering}
    \end{figure*}

    \section{Paper Reproducibility}
    In order to facilitate reproducibility we make source code for the paper and figures  available at \url{https://github.com/jolideco/jolideco-paper}.
    The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021}. See instructions 
    All data is available on Zenodo \todo{how do we do this exactly...?}

    For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow \footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.

    For the Chandra data reduction we used a custom \texttt{Snakemake} workflow \footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.

@@

    \begin{itemize}
        \item Extend \jolideco to handle spectral dimension at the same time.
        \item Use normalising flows for patch priors see \cite{Altekrueger2022}
        \item Use other mixture models, such as Student T or generalised Gaussian. 
        \item one could try deep image priors \citep{Ulyanov2017}
        \item Extend to use GMM patch prior on multiple scales, see \cite{Papyan2015}
        \item Exclude point sources either via separate component or "J-invariance"
    \end{itemize}

    \section*{Acknowledgements}
    This work was conducted under the auspices of the CHASC International Astrostatistics Center.
    CHASC is supported by NSF grants DMS-21-13615, DMS-21-13397, and DMS-21-13605; by the UK Engineering
    and Physical Sciences Research Council [EP/W015080/1]; and by NASA APRA Grant 80-NSSC21-K0285.

    We thank CHASC members for many helpful discussions, especially Xiao-Li Meng and Katy McKeough.
    DvD was also supported in part by a Marie-Skodowska-Curie RISE Grant (H2020-MSCA-RISE-2019-873089)
    provided by the European Commission.

    Aneta Siemiginowska, Vinay Kashyap, and Doug Burke further acknowledge support from NASA
    contract to the Chandra X-ray Center NAS8-03060.

    Some of the computations in this paper were conducted on the Smithsonian High Performance
    Cluster (SI/HPC), Smithsonian Institution \url{https://doi.org/10.25572/SIHPC}.
